Demes: a specification for interchanging complex demography

### 2021-06-15 paper.tex
Update author list and title.

\title{\demes: a pain-free specification for complex demography}
\author[*]{Graham Gower}
\author[*]{Aaron P. Ragsdale}
\author[ ]{...Others here...}
\author[**]{Jerome Kelleher}
\author[**]{Kevin Thornton}
\affil[*,**]{Denote equal contribution}
\maketitle

\abstract{
}

>>>>

\title{Demes: a specification for interchanging complex demography}
% First authors
\author[1,$\star$]{Graham Gower}
\author[2,$\star$]{Aaron P. Ragsdale}

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Ryan N. Gutenkunst}
\author[4]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[3]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen}
\affil[2]{FIXME: Aaron's affiliation}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Evolutionary Biology, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California at Irvine}

\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\aleph$]{Denotes corresponding authors}

\maketitle

\abstract{}
